### 2023-06-15 application.tex
up

\begin{proposition}
{\sc Bounded resilience} and {\sc $k$-resilience} never hold for vector addition system when $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$
\end{proposition}

@@

\begin{proof}
When asking about {\sc Resilience}, in context, there are no true ``neutral'' configurations.
Indeed, from a VASS $V$, $\Safe$ and $\Bad$ semilinear, one can build VASS $V'$, $\Safe'$ semilinear, and $\Bad'$ complement of $\Safe'$ such that {\sc Resilience} holds for
$V$, $\Safe$ and $\Bad$ if and only if {\sc Resilience} holds for
$V'$, $\Safe'$ and $\Bad'$. For the construction, $V'$ will have two copies of the control states of $V$; $Q_{A}$ and $Q_{B}$, and will have two other VASS running in parallel checking whether or not the current configuration belong to $\Safe$ resp. $\Bad$. 
From a configuration with state in $Q_{A}$ you go to $Q_B$ when you are in a $\Bad$ place
and from a configuration with state in $Q_{B}$ you go to $Q_{A}$ when you are in a $\Safe$ place.
$\Safe'$ is $Q_A \times \N^d$ and $\Bad'$ is $Q_B \times N^d$.

Without loss of generality hence let us consider only the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).\]
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

Resilience is also decidable for other class of counter machines for which the reachability relation can be expressed in a decidable logics. Recall that lossy counter machines \cite{DBLP:conf/rp/Schnoebelen10} are counter machines that may loose tokens in each control-state.

>>>>

@@

\begin{proof}
\iffalse When asking about {\sc Resilience}, in context, there are no true ``neutral'' configurations.
Indeed, from a VASS $V$, $\Safe$ and $\Bad$ semilinear, one can build VASS $V'$, $\Safe'$ semilinear, and $\Bad'$ complement of $\Safe'$ such that {\sc Resilience} holds for
$V$, $\Safe$ and $\Bad$ if and only if {\sc Resilience} holds for
$V'$, $\Safe'$ and $\Bad'$. For the construction, $V'$ will have two copies of the control states of $V$; $Q_{A}$ and $Q_{B}$, and will have two other VASS running in parallel checking whether or not the current configuration belong to $\Safe$ resp. $\Bad$. 
From a configuration with state in $Q_{A}$ you go to $Q_B$ when you are in a $\Bad$ place
and from a configuration with state in $Q_{B}$ you go to $Q_{A}$ when you are in a $\Safe$ place.
$\Safe'$ is $Q_A \times \N^d$ and $\Bad'$ is $Q_B \times N^d$.

Without loss of generality hence let us consider only \fi
We consider the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
\[\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).\]
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

Resilience is also decidable for other class of counter machines for which the reachability relation can be expressed in a decidable logic. Recall that lossy counter machines \cite{DBLP:conf/rp/Schnoebelen10} are counter machines that may loose tokens in each control-state.
